### 2014-10-22 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: minor formatting changes
DelCo 2012: Added table, some formatting.

				\begingroup
				\hypersetup{urlcolor=black}
				\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
				\endgroup

				August 2014}}

@@

@@

	Two identical concrete structures were built on a concrete slab as shown in Figure 1. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.  The interior dimensions of teach structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

@@

	The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed “floor assembly”.  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

@@

	In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter’s head.  One of the gauge’s sensing surface is facing the ceiling and the other gauge is facing the pallets.  A similar heat flux gauge installation is located in the hallway, approximately 3.81 m (12.5 ft) from the burn room and 0.3 m (1ft) from the east wall of the hallway as shown in figure xx.  Again on gauge was facing the ceiling and one was facing the burn room.

@@

	The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood “floor assembly”.
	Two stacks of pallets with hay were used as the first items ignited in each experiment.  Each stack was composed of six pallets with a half bale of hay.  The hay was layered between each pallet.  The pallets and hay were weighed prior to each experiment.  For the four experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4 kg (511.3 lbs).  A complete listing of the mass of each pallet and hay bales is given in Appendix ????????

	The pallet stacks were located 0.3 m (1ft) away from the east and south walls of the burn room.  The pallets were 1.2 m (48 in) long, 1.0 m (40 in ) and 123 mm (4.8 in) high.  The stacks were 150 mm (6 in) apart.  One layer of 13 mm (0.5 in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
	The east and south wall of the burn room was covered with 15 mm (0.59 in) thick, sheets of plywood.  The “wood flooring assembly”, composed of 12 TGIs and 9 sheets of OSB, served as the ceiling of the burn room.  The open doorway to the burn room on the south side was covered with a 2.4 m (8 ft) tall by 1.2 m (4 ft) wide piece of medium density fiberboard paneling that was 5 mm (0.19 in) thick.  The southeast corner of the burn room with the fuel load installed is shown in Figure 3.

@@

>>>>

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

\vspace*{2\baselineskip}
August 2014}}

@@

\vspace{0.2in}

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
\endgroup

@@

Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.  The interior dimensions of teach structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

@@

The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed ``floor assembly".  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

@@

In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter's head.  One of the gauge's sensing surface is facing the ceiling and the other gauge is facing the pallets.  A similar heat flux gauge installation is located in the hallway, approximately 3.81 m (12.5 ft) from the burn room and 0.3 m (1ft) from the east wall of the hallway as shown in figure xx.  Again on gauge was facing the ceiling and one was facing the burn room.

@@

The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly". Two stacks of pallets with hay were used as the first items ignited in each experiment.  Each stack was composed of six pallets with a half bale of hay.  The hay was layered between each pallet.  The pallets and hay were weighed prior to each experiment.  For the four experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).  A complete listing of the mass of each pallet and hay bales is given in Appendix ????????

The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room.  The pallets were 1.2~m (48~in) long, 1.0~m (40~in) and 123~mm (4.8~in) high.  The stacks were 150~mm (6~in) apart.  One layer of 13 mm (0.5 in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
The east and south wall of the burn room was covered with 15~mm (0.59~in) thick, sheets of plywood.  The ``wood flooring assembly", composed of 12 TGIs and 9 sheets of OSB, served as the ceiling of the burn room.  The open doorway to the burn room on the south side was covered with a 2.4~m (8~ft) tall by 1.2~m (4~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.19~in) thick.  The southeast corner of the burn room with the fuel load installed is shown in Fig.~\ref{fig:Wood_Fuel_Load}.

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
		2 (FSW2)   	& 302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
		3 (FSW3) 	&  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
		4 (FSE4)    &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
		5 (FSE5)    &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
		6 (FSW6)    &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
		7 (FSW7)    &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
		8 (FSE8)    &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
		9 (Attic 1) &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
		10 (Attic 2)&  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
		11 (FSE1)   &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
		12 (FSW1)   &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
		13 (FSE2)   &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
		14 (FSW2)   &  Cotton w/ inner springs          &                            &  4.06 kg    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}
